On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-07-13 documents/paper.tex
Austinman request

@@

estabilishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately the X-Band, around 7-10 GHz.

@@

\lettrine{It} cannot be overstated how unexpected and dubious this finding appears to be -at least, based on our limited research and experience to date.

@@

If this mechanism exists, it would seem to provide the following advantages over other methods such as UV or cold-plasma sterilization:

\begin{itemize}
  \item This is a non-ionizing, non-thermal
%
\footnote{It may be useful to define 'non-thermal'; it caused us some confusion. Certainly the proteins of the virion locally absorb energy and increase in temperature. The key is that, when excited in this manner, the energies in the envelope are poorly modelled by a Maxwell-Boltzmann distribution; they are not given sufficient time to 'thermalize'. In contrast, with typical 2.4 GHz microwave exposure, sterilization can only occur by aggregate heating of the fluid and tissue.}
%
, non-chemical technique, harmless for continuous exposure to tissue, which produces no ozone, can be effective inside bodily tissues, and can readily be produced with \$1 - scale devices.

  \item Potentially far-field and moderately penetrating inactivation. 
  \item

\end{itemize}

@@

\begin{toolchain}
	{\it \bf [Yang 2015]'s toolchain}
	\begin{itemize}
	\item Envelope/liposome breaking strength and stiffness from AFM nanoindentation data
	\item Analytical expression assuming homogenous sphere for microwave absorption cross-section
	\item Experimental absorption data from microwave cuvette -> 
	\item COMSOL finite-element for illustration
	\end{itemize}
\end{toolchain}

@@

Other physiological effects include changes in the permeability of membranes, direct nerve stimulation, and others. These are all accounted for in the time-domain equation and the 6-minute averaging period.

This would seem to open an obvious route of optimization. If the virus is destroyed in tens of nanoseconds - essentially governed by instantaneous power. But tissue damage requires *energy deposition*.

@@

\paragraph{\textbf{Direct treatments}}\

[Hand 1982] $E_{mag}=1/e$ (13.5\% power density) skin\footnote{electromagnetic skin, not tissue skin}\footnote{well, both, I suppose.} depth is approximately:

\begin{center}
\begin{tabular}{|l|l|l|}
\hline
F=10 GHz          & Dry tissue & Wet tissue \\ \hline
Penetration depth & 30 mm      & 5 mm \\ \hline
\end{tabular}
\end{center}

SARS is found widely distributed throughout the most favorable organs [Ding 2004], shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.

However, destruction of lung tissue appears to be the primary cause of death via SARS [Nicholls 2006].

@@

@@

Luckily, this project falls perfectly within the subset of microwave technologies that do not require a goatee. The vast majority of the behavior of most circuits can be modelled with the very same SPICE tools as one would use at low frequencies. With judicious application of reference designs, it seems to be possible to design

@@

We've got a thing 
that's called 
Radar Love
We've got a wave
in the air
Radar Love

>>>>

We've got a thing 
that's called 
Radar Love
We've got a wave
in the air

The phased-array techdemo.

@@

estabilishes that - unique to certain viruses, and apparently unlike human cellular structures, as we shall see - coincidentally have just the right size, shape, stiffness, and net charge distribution to form a weak (Q=2) spherical dipole resonance mode which couples well to the microwave spectrum at approximately the X-Band, at around 8 GHz.

@@

If this mechanism exists, it would seem to provide significant advantages over existing UV or cold-plasma sterilization.

If the extensions made in our paper are valid, this is a non-ionizing, non-thermal
%
\footnote{It may be useful to define 'non-thermal'; it caused us some confusion. Certainly the proteins of the virion locally absorb energy and increase in temperature. The key is that, when excited in this manner, the energies in the envelope are poorly modelled by a Maxwell-Boltzmann distribution; they are not given sufficient time to 'thermalize'. In contrast, with typical 2.4 GHz microwave exposure, sterilization can only occur by aggregate heating of the fluid and tissue.} 
%
, non-chemical technique, harmless for continuous exposure to tissue, produces no ozone, can readily be produced with \$1 - scale devices.

Moreover, it would act instantaneously, and - perhaps most critically - could be made to act {\bf within infected tissues}; and is minimally absorbed by air, allowing action in the far-field, scaling to square-kilometer areas with single installations.

\begin{autem}

{\it autem}\\

That paragraph may cut an impressive figure; but recall that the rest of this paper

\end{autem}

\lettrine{It} cannot be overstated how unexpected and positively dubious this finding appears to be -at least, based on our limited research and experience to date.

@@

@@

@@

Other physiological effects include changes in the permeability of membranes, direct nerve stimulation; these are all accounted for in the time-domain equation and the 6-minute averaging period.

To drive home this point, apparently the best-quality evidence available fulfills sham requirements [Vijayalaxmi 2006] provide in-vitro. They expose blood lymphocytes to pulse power  in precisely the regime required in this work; 8.2 GHz, 8 ns duration and 50 khz repetition rate, pulse power densities of 250,000 $W/m^2$\footnote{computed from average power / duty cycle}, for 2 hours, and find no genotoxicity. [Chemeris 2004] use 8.8 GHz, 180 ns pulse width, peak power 65,000 W , repetition rate 50 Hz, exposure duration 40 min, on frog etheyrocytes?

So it appears that this is not merely rules-lawyering to exploit a loophole in the regulations; it is a physically-informed effect.

\begin{autem}

These papers (the best quality we are aware of) were extensively cherry-picked from the literature based on the results of a meta-analysis [Vj. 2019], listing the requirements for reliable in-vitro RF experiments.\\

How sensitive this research is, [Chemeris 2004] mention:\\

"The increase in DNA damage after exposure of cells to HPPP EMF shown in Table 2 was due to the temperature rise in the cell suspension by 3.5±0.1 ◦C. This was confirmed in sham-exposure experiments and experiments with incubation of cells for 40 min under the corresponding temperature conditions."\\

There are a substantial number of papers in the literature which show positive effect sizes; these are listed in the bibliography. \\

The literature reviews conducted by standards organizations.\\

We are not aware of any past uses of these microwave en-masse. We do not have the

\end{autem}

This would seem to open an obvious avenue of optimization. If the virus is destroyed in tens of nanoseconds - essentially governed by instantaneous power. But tissue damage requires *energy deposition*.

@@

\paragraph{\textbf{Direct treatments at the fundamental}}\

Via [Hand 1982], the $E_{mag}=1/e$ penetration depth\footnote{"skin skin depth?"} is approximately 40 mm for 'dry' tissues and 5 mm for 'wet'.

SARS is found widely distributed throughout many of the most favoured organs [Ding 2004], shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.

However, destruction of lung tissue appears to be significant in the lethality of SARS [Nicholls 2006].

@@

\paragraph{\textbf{Subharmonics}}\

The 8 GHz wave need not be the fundamental. A modulated carrier wave with a more deeply penetrating wavelength which then locally interferes to produce the 8 GHz tone within the tissue could be useful.

The penetration depth shortens as frequency increases, until the so-called 'optical windows' in the absorption spectra of tissues, particularly in the near-IR range.

@@

Luckily, this project falls perfectly within the subset of microwave technologies that do not require a goatee. The vast majority of the behavior of most circuits can be accurately modelled with the very same SPICE tools as one would use at low frequencies. With judicious application of reference designs, it seems to be possible to design

@@

### 2020-07-13 documents/supplemental.tex
Austinman request

@@

>>>>

Th edges are charred; however, we have not found any discussion of toxicity of the laser cut edges, so we assume they're fine.

@@

Not all plastics can be laser welded.

One problem with the formal, academic paper format is that one starts to believe what is written, which is a death sentence for accurate reasoning. We try to avoid this by being unprofessional.
